### 2016-01-20 ch06-concl/conclusions.tex
Small changes
Add epigraphs

\chapter{Conclusions}

@@

  \subsection{Excitation design}
  In this thesis, multisine signals are proposed to measure \gls{SISO} systems within an \gls{LTI} framework.
  Particularly, the proposed multisine signals employ a quasi-logarithmic frequency grid and a power spectrum in $1/f$ akin to pink noise to ensure a good quality of the \gls{FRF} over the whole excited frequency band.
  As such, they are more robust excitation signal than e.g. typical general-use signals such as linear grid multisines or white noise excitation with the same total signal power and duration.
  In this thesis it has been proven that when the user has prior knowledge about the expected minimal damping $\damping_{\min}$ of the poles present in the system, this sets the required logarithmic frequency grid spacing to attain a guaranteed relative uncertainty of the identified \gls{FRF} near the resonance peaks.
  Concretely, the grid spacing $\alpha \isdef \frac{f_{k+1}}{f_k}$ of the (quasi-)logarithmic grid should conform to
  \begin{equation}
    \alpha \leq 1 + \damping_{\min}
  \end{equation}
  to attain a reliable estimate of the resonances present in the system.
  The choice to use the equality $\alpha = 1+ \damping_{\min}$ is the optimal choice within the framework present in \chapref{sec:excitation}. 
  Decreasing $ \alpha$ further comes at the cost of more excited frequency bins and consequently a lower power per bin, or, a reduced \gls{SNR} per bin if the overall signal power is limited as in many cases.

@@

\section{Future research}
  \subsection{Excitation design}
  In this thesis, quasi-logarithmic multisines were proposed as a robust excitation signal that provide efficient estimation of sharp resonance peaks in the \gls{SISO} case.
  Obviously, a first important extension of this research is towards the \gls{MIMO} case which is more involved.
  To measure \gls{MIMO} systems using multisines, one of two typical approaches is often followed when measuring all channels at the same time:
  \begin{itemize}
    \item Zippered multisines, where the frequency grids of the different input channels are interspersed. This has the downside that frequency resolution is traded in for computational simplicity and that the different entries in the \gls{FRF} matrix are known on different frequency grids.
    \item Orthogonal multisines, which are computationally more involved to process.
  \end{itemize}
  Due to the intrinsic sparsity of quasi-logarithmic grids, however, zippered quasi-logarithmic multisines might offer a very easy and elegant  approach to measure \gls{MIMO} systems with a moderate number of inputs.

>>>>

\chapter{Conclusions}
\myEpigraph{Life can only be understood backwards; but it must be lived forwards.}{Søren Kierkegaard}{}

@@

  \subsection{Excitation design}
  In this thesis, multisine signals are proposed to measure \gls{SISO} systems within an \gls{LTI} framework.
  Particularly, the proposed multisine signals employ a quasi-logarithmic frequency grid and a power spectrum in $1/f$ akin to pink noise to ensure a good quality of the \gls{FRF} over the whole excited frequency band.
  As such, they are more robust excitation signal than e.g. typical general-use signals such as linear grid multisines or white noise excitation with the same total signal power and duration.
  In this thesis it has been proven that when the user has prior knowledge about the expected minimal damping $\damping_{\min}$ of the poles present in the system, this sets the required logarithmic frequency grid spacing to attain a guaranteed relative uncertainty of the identified \gls{FRF} near the resonance peaks.
  Concretely, the grid spacing $\alpha \isdef \frac{f_{k+1}}{f_k}$ of the (quasi-)logarithmic grid should conform to
  \begin{equation}
    \alpha \leq 1 + \damping_{\min}
  \end{equation}
  to attain a reliable estimate of the resonances present in the system.
  The choice to use the equality $\alpha = 1+ \damping_{\min}$ is the optimal choice within the framework presented in \chapref{sec:excitation}. 
  Decreasing $ \alpha$ further comes at the cost of more excited frequency bins and consequently a lower power per bin, or, a reduced \gls{SNR} per bin if the overall signal power is limited as in many cases.

@@

\section{Future perspectives}
  \subsection{Excitation design}
  In this thesis, quasi-logarithmic multisines were proposed as a robust excitation signal that provide efficient estimation of sharp resonance peaks in the \gls{SISO} case.
  Obviously, a first important extension of this research is towards the \gls{MIMO} case which is more involved.
  To measure \gls{MIMO} systems using multisines, one of two typical approaches is often followed when measuring all channels at the same time:
  \begin{itemize}
    \item Zippered multisines, where the frequency grids of the different input channels are interspersed. This has the downside that frequency resolution is traded in for computational simplicity and that the different entries in the \gls{FRF} matrix are known on different frequency grids.
    \item Orthogonal multisines, which are computationally more involved to process.
  \end{itemize}
  Due to the intrinsic sparsity of quasi-logarithmic grids, however, zippered quasi-logarithmic multisines might offer a very easy and elegant  approach to measure \gls{MIMO} systems with a moderate number of inputs.
